Transfer Learning in Multimodal Compositional and Relational Reasoning

### 2019-11-15 cvpr_submission/experiments.tex
Typo.
Some minor typo corrections in COG section 5.2.2.

Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (dark blue). Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).

Nevertheless, significant accuracy gains are noted when training jointly on all tasks (light gray), ranging from 18 points to 37 points on 4 out of 5 tasks. \textit{QueryAttribute} only sees an increase of one point. One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks. These improvements suggest that related tasks benefit from joint training.
%We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task). We hypothesize that the improvements on e.g. \textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e., labels domain).

@@

We then conducted the following experiments using the Canonical variant of COG to study 
whether transfer learning was effective in leveraging information gained by training a task family at a higher level
of the hierarchy.
 \begin{itemize}
 	\compresslist
	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (standard ML). 
	\item Train on \textbf{Group A} and test on \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare} each;
	\item Train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
	can be viewed as training on \textbf{All} and testing on each group at the leaf level separately.
\end{itemize}

@@

First notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases 
suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
With \textbf{Spatial} we see a small improvement showing that there is some benefit due to joint training with other task families.
Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
The former saw an accuracy jump from 68.6\% by training on samples from that family alone
to 97.0\% while training on all samples. To furthe rdrill down on this behavior, notice that 
just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
In hindsight, this is not surprising because the questions in \textbf{Compare} are composed
of fragments in the questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
Lastly, for the  \textbf{Spatial} family we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
is a slight loss incurred by including everything. As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in the accuracy (97.1\%). To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\columnwidth]{img/results/CoGenT_B_results.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and finetuning on CoGenT-B (gray).}
	\label{fig:CoGenT-B-results}
\end{figure}
Evaluating SAMNet on CoGenT shows that performance is worse on CoGenT-B than CoGenT-A, in line with~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}. Finetuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A, also observed in other models.

>>>>

Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue). Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).

Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks. \textit{QueryAttribute} only sees an increase of one point. One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks. These improvements suggest that related tasks benefit from joint training.
%We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task). We hypothesize that the improvements on e.g. \textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e., labels domain).

@@

We then conducted the following experiments using the Canonical variant of COG to study 
whether transfer learning was effective in leveraging information gained by training a task family at a higher level
of the hierarchy:
 \begin{itemize}
 	\compresslist
	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (standard ML). 
	\item Train on \textbf{Group A} and test on \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare} each;
	\item Train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
	can be viewed as training on \textbf{All} and testing on each group at the leaf level separately.
\end{itemize}

@@

First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
The former saw an accuracy jump from 68.6\% by training on samples from that family alone
to 97.0\% when training on all samples. To further emphasize this behavior, notice that 
just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
In hindsight, this is not surprising as the questions in \textbf{Compare} are composed
of fragments of the questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
is a slight loss incurred by including everything. As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%). To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\columnwidth]{img/results/CoGenT_B_results.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and finetuning on CoGenT-B (gray).}
	\label{fig:CoGenT-B-results}
\end{figure}
Evaluating SAMNet on CoGenT shows that performance is worse on CoGenT-B than CoGenT-A, in line with~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}. Finetuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A, also observed with other models.
